Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-07-01 Paper/paper.tex
simple calc more

\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}

@@

threshold at which a source is considered detectable~\footnote{which

@@

where $N_i$ is the number of sources within the $i-$th shell (such that
$N:=\sum N_i$), and $n$ is the number density of source distribution in volume.

@@

>>>>

% \textbf{Multiple identical sources at low SNR: }
\label{s2:identical_multiple}

@@

threshold $\rho_\mathrm{min}$ at which a source is considered
detectable~\footnote{which

@@

where $N_i$ is the number of sources within the $i-$th shell (s.t.
$N:=\sum N_i$), and $n$ is the number density of sources in volume.

@@

While we discussed Eq.~\ref{eq:rmsSigmaIdenticalSources} for a population
of optimally oriented sources, it is valid more generally if the population is
distributed uniformly in {\it effective} volume~\footnote{{\it effective} 
distance $D_\mathrm{eff}$ 
is a combination of distance to the source, its orientation, and its sky
location angles, and has a one-to-one correspondence with SNR for non-precessing
systems, for which these angles are constant in time. Effective volume is 
proportional to the $D_\mathrm{eff}^3$}~\cite{Markakis:2010mp}. However, it 
still only applies to sources with identical masses and spins, and we 
overcome this limitation by performing a fully Bayesian analysis next.
